---
title: "Assignment 13"
author: "Tofiga Abdiyeva"
date: today
format:
  html: 
    toc: true
    toc-depth: 2
    toc-title: contents
    toc-location: left
    smooth-scroll: true
number-sections: true
number-depth: 2
title-block-banner: true
code-fold: true
theme: quartz
execute:
  echo: fenced
  warning: false
output: html_document
---

```{r}
load("../Data/.RData")
```

# Severence - Season 1 summary in numbers

### __(*Warning:* spoilers ahead)__

***

### Overview

(From the [Wikipedia](https://en.wikipedia.org/wiki/Severance_(TV_series)) Severance is an American science fiction psychological thriller television series created by Dan Erickson and directed by Ben Stiller and Aoife McArdle. It stars Adam Scott, Zach Cherry, Britt Lower, Tramell Tillman, Jen Tullock, Dichen Lachman, Michael Chernus, John Turturro, Christopher Walken, and Patricia Arquette. The plot follows Mark (Scott), an employee of Lumon Industries who agrees to a "severance" program in which his non-work memories are separated from his work memories.

Biotechnology corporation Lumon Industries uses a mindwipe medical procedure called "severance" to separate the consciousness of their employees between their lives at work and outside of it. Due to their increasingly divergent life experiences, the consciousnesses of the employees in the work place (dubbed "innies") gradually split from their consciousnesses outside of it (dubbed "outies"), to the point that they become distinct personalities with their own agendas. One severed employee, Mark (Adam Scott), gradually uncovers a web of conspiracy at Lumon, and the mysterious project the employees are unknowingly working on.



***

### Epsiode 1 summary

Mark Scout, who works in Lumon Industries's Macrodata Refinement (MDR) division, discovers he is being promoted to department head in light of coworker Petey's sudden departure. His first task is to orientate Helly, the replacement, who wakes up in a conference room with no memory of who or where she is. After being given an orientation and learning her name, she demands and is allowed to leave but finds she is unable to do so. She then sees a video explaining that she has undergone the "severance" procedure, which split her memories to create a version of herself that will only exist inside the workplace. The "outside" version of Mark, a former professor grieving his wife's death and living in the Lumon-subsidized town of Kier, encounters a man claiming to be Petey who gives him a letter with cryptic instructions. Mark returns home and interacts with his neighbor Mrs. Selvig, unaware that she is his boss, senior manager Harmony Cobel.

TRelatively recent media that influenced Severance include the online urban legend known as The Backrooms, the computer game The Stanley Parable, films including Office Space, Brazil, The Truman Show, and Eternal Sunshine of the Spotless Mind, and the Dilbert comic strips.[37] Older influences include the existential hell in the Jean-Paul Sartre play No Exit and the totalitarian dystopia in the George Orwell novel Nineteen Eighty-Four.[38] Aesthetically, the series was influenced by the films Brazil, Dark City, and Playtime.
***

You can see how the viewership of the episodes changed in Figure 1.

```{r}
#| label = "viewers_plot"
plot(season_data$viewers, type="l", col="red", lwd=3, xlab = "Char name", ylab = "Real name")
```

***



